From Stone to Tool: How Raw Materials Influenced Upper Paleolithic Technology in Southwestern Iberia (Vale Boi)

### 2025-05-06 analysis/paper/paper.qmd
Improvements
Added ggsave codes for future graph saving

**Author contributions:** Study conception and design were performed by Joana Belmiro and João Cascalheira. Material preparation, data collection, database collection and treatment and analysis were performed by Joana Belmiro. The first draft of the manuscript was written by Joana Belmiro and all authors commented on previous versions of the manuscript. All authors read and approved the final manuscript.

@@

@@

@@

@@

@@

>>>>

**Author contributions:** Study conception and design were performed by Joana Belmiro, Nuno Bicho and João Cascalheira. Material preparation, data collection, database collection and treatment and analysis were performed by Joana Belmiro. The first draft of the manuscript was written by Joana Belmiro and all authors commented on previous versions of the manuscript. All authors read and approved the final manuscript.

@@

#ggsave("general_graphs.png", width = 6, height = 8, units = "in", dpi = 300, bg = "white")

@@

#ggsave("ratios.png", width = 6, height = 7, units = "in", dpi = 300, bg = "white")

@@

#ggsave("gravettian_plots.png", width = 6, height = 6, units = "in", dpi = 300, bg = "white")

@@

#ggsave("proto_plots.png", width = 6, height = 6, units = "in", dpi = 300, bg = "white")

@@

#ggsave("solutrean_plots.png", width = 6, height = 6, units = "in", dpi = 300, bg = "white")
